Soling at the 2000 Summer Olympics

### 2020-07-27 inst/f1points.Rmd
more work

@@

@@

>>>>

\begin{multline}
\mbox{Hamilton}\succ
\mbox{Vettel}\succ
\mbox{Bottas}\succ
\mbox{Raikkonen}\succ
\mbox{Ricciardo}\succ
\mbox{Verstappen}\succ\\
\mbox{Perez1}\succ
\mbox{Ocon}\succ
\mbox{Sainz}\succ
\mbox{Hulkenberg}\succ
\mbox{Massa}
\end{multline}

@@

\begin{multline}
\mbox{Hamilton}\succ
\mbox{Vettel}\succ
\mbox{Bottas}\succ
\mbox{Ricciardo}\succ
\mbox{Verstappen}\succ
\mbox{Raikkonen}\succ\\
\mbox{Perez}\succ
\mbox{Ocon}\succ
\mbox{Massa}\succ
\mbox{Sainz}\succ
\mbox{Hulkenberg}\succ
\end{multline}

@@

We can now calculate number of places agreed for each of the points systems:

```{r, label=calcpoints_allpointsystems, echo=FALSE, cache=TRUE}
agreement2016 <- rep(NA,length(formula1_points_systems(top)))
agreement2017 <- rep(NA,length(formula1_points_systems(top)))
agreement2018 <- rep(NA,length(formula1_points_systems(top)))
agreement2019 <- rep(NA,length(formula1_points_systems(top)))

for(i in seq_along(formula1_points_systems(top))){

  pa <- formula1_points_systems(top)[[i]]

  dp2016a <- ordertable2points(as.ordertable(F1_table_2016[seq_len(top),]),pa)
  dp2016a <- sort(dp2016a,decreasing=TRUE)
  dp2016a[] <- seq_along(dp2016a)
  agreement2016[i] <-  sum(cumprod(names(dp2016a) == names(m2016)))

  dp2017a <- ordertable2points(as.ordertable(F1_table_2017[seq_len(top),]),pa)
  dp2017a <- sort(dp2017a,decreasing=TRUE)
  dp2017a[] <- seq_along(dp2017a)
  agreement2017[i] <-  sum(cumprod(names(dp2017a) == names(m2017)))

  dp2018a <- ordertable2points(as.ordertable(F1_table_2018[seq_len(top),]),pa)
  dp2018a <- sort(dp2018a,decreasing=TRUE)
  dp2018a[] <- seq_along(dp2018a)
  agreement2018[i] <-  sum(cumprod(names(dp2018a) == names(m2018)))

  dp2019a <- ordertable2points(as.ordertable(F1_table_2019[seq_len(top),]),pa)
  dp2019a <- sort(dp2019a,decreasing=TRUE)
  dp2019a[] <- seq_along(dp2019a)
  agreement2019[i] <-  sum(cumprod(names(dp2019a) == names(m2019)))

}  # i loop closes

agreement4yearsallp <- cbind(
    agreement2016,
    agreement2017,
    agreement2018,
    agreement2019
)

rownames(agreement4yearsallp) <- names(formula1_points_systems(top))
colnames(agreement4yearsallp) <- 2016:2019
```

```{r}
agreement4yearsallp
```
